\chapter{The Forgotten Sector}

In the previous chapters, we immersed ourselves in an idealized geometric world. On that flawless Dirac circle, vectors merely engaged in elegant zero-sum games between ``external motion'' ($v_{ext}$) and ``internal evolution'' ($v_{int}$). That was a reversible, eternal, dissipationless crystal universe.

However, we must honestly face reality: that is not the universe we live in.

Our world is full of broken teacups, extinguished fires, and forgotten memories. Beyond that perfect two-dimensional circular plane, there must exist a dark abyss, constantly devouring ordered information.

This chapter will unveil that third dimension we have long ignored. We will see that the perfect circle has not truly disappeared; it has merely ruptured in a higher dimension, opening a gate to an invisible ``shadow sector.''

\section{The Perfect Circle Ruptured}

\begin{quote}
``The universe not only has `internal' and `external'; the universe also has a bottomless pocket. We call it `environment,' but it is actually a backdoor to infinite dimensions.''
\end{quote}

\subsubsection{The Emergence of the Third Axis}

In the previous two volumes, we simplified the core formula to $v_{ext}^2 + v_{int}^2 = c_{FS}^2$. This is a conservation law for closed systems. It assumes the system is completely isolated from the rest of the universe.

But in the complete picture of \textbf{Vector Cosmology}, no system is a true island. The tangent space of projective Hilbert space does not have only two orthogonal subspaces. According to our strict definition in the paper, the tangent space $T_{[\psi(\tau)]}P(\mathcal{H})$ is decomposed into three parts:

\[V_{total} \simeq V_{ext} \oplus V_{int} \oplus V_{env}\]

This introduces the third crucial velocity component---\textbf{Environment Velocity ($v_{env}$)}. It represents the projection rate of the global vector onto those degrees of freedom we cannot track or control (such as heat baths, vacuum fluctuations, stray photons).

Thus, that simple two-dimensional circle equation is extended to a three-dimensional sphere surface equation---we call it the \textbf{``Extended Capacity Identity''}:

\[v_{ext}^2 + v_{int}^2 + v_{env}^2 = c_{FS}^2\]

\subsubsection{Information Leakage and Circle Shrinkage}

The emergence of this new formula announces the ``rupture'' of the perfect circle.

For a local observer (such as ourselves), we can usually only observe $v_{ext}$ (object motion) and $v_{int}$ (object mass/structure). We cannot see $v_{env}$ because ``environment'' is by definition those degrees of freedom that escape our observation range.

When we ignore $v_{env}$, the original conservation law becomes an inequality:

\[v_{ext}^2 + v_{int}^2 = c_{FS}^2 - v_{env}^2 \le c_{FS}^2\]

In our view, this manifests as \textbf{``shrinkage of effective budget''}.

\begin{itemize}
\item When $v_{env}$ increases (i.e., the system becomes entangled with the environment), the shares left for $v_{ext}$ and $v_{int}$ must decrease.

\item Geometrically, this means the circle we see on the $(v_{ext}, v_{int})$ plane is continuously shrinking in radius.
\end{itemize}

This is the geometric essence of \textbf{dissipation}.

A rolling ball eventually stops ($v_{ext} \to 0$), a cup of hot water eventually cools ($v_{int}$ decreases), not because energy disappears into thin air, but because the \textbf{$c_{FS}$ budget} carrying energy irreversibly rotates orthogonally from the visible ``internal/external'' sectors to the invisible ``environment'' sector.

\subsubsection{The Invisible Shadow}

Why do we call it the ``forgotten sector''?

Because in the vast majority of physical equations, we try to idealize systems, pretending $v_{env} = 0$. We write perfect Hamiltonians and draw closed orbits.

But in \textbf{Vector Cosmology}, $v_{env}$ is not an error term; it is one of the protagonists of cosmic evolution.

\begin{itemize}
\item \textbf{It is noise}: In quantum walk experiments, it is the culprit causing data points to fall into the ``forbidden zone.''

\item \textbf{It is entanglement}: It is the ``connection fee'' the system pays to integrate into the whole universe.

\item \textbf{It is entropy}: As we will see in the next section, $v_{env}$ is the geometric source of the second law of thermodynamics.
\end{itemize}

The perfect circle has ruptured, but it ruptured so magnificently. It is no longer a closed ring but has become a spiral open to infinite dimensions. It is precisely because of this gap that the universe has heat, death, and time's irreversible sorrow.

