\section{6.2 The Rewriting of Physical Laws}

\begin{quote}
``When speed is fast enough to ignore distance, `position' is no longer a physical quantity, but just a memory address. In the universe of $\tau = 2000$, Newton's mechanics and Einstein's relativity are not overthrown; they are `dimensionally reduced.' They become outdated syntax in that grander holographic operating system, applicable only to low-speed subroutines.''
\end{quote}

In the previous section, we predicted that at $\tau = 2000$, effective light speed will explode by $10^{13}$ times. This means the Milky Way is causally compressed into a single quantum state with instant response capability.

This order-of-magnitude change is not merely parameter adjustment; it is \textbf{physical picture reconstruction}.

The physical laws we learn in textbooks---$F=ma$, $E=mc^2$, $G=mM/r^2$---all share a common premise: \textbf{Locality}. They assume objects must interact by traversing space, and this interaction is limited by distance.

But when light speed $c$ tends toward infinity (relative to macroscopic scales), locality fails. Physics will transform from \textbf{``the science of motion''} to \textbf{``the science of information''}.

\subsection{From Transport to Teleportation: The Abolition of $v_{ext}$}

In old physics, if you want to send an apple from Earth to Mars, you need to overcome gravity, burn fuel, spend time. You are paying expensive \textbf{$v_{ext}$ (external velocity)} budget to exchange for spatial coordinate translation.

But in the high light-speed era, this kind of \textbf{``physical transport''} appears extremely primitive and inefficient.

As $c(\tau)$ grows exponentially, the cost of transmitting information (energy consumption/time) decreases exponentially relative to transporting matter. Civilization will discover a new axiom:

\textbf{``Moving atoms is foolish; moving bits is wise.''}

Physical laws are rewritten as \textbf{Quantum Teleportation Protocol}:

\begin{enumerate}
\item \textbf{Scan}: Read the \textbf{$v_{int}$ (internal structure)} information (quantum state) of the apple at the source point.

\item \textbf{Transmit}: Use extremely high-bandwidth entanglement channels to instantly send these classical and quantum information to the destination.

\item \textbf{Reconstruct}: At the destination, use local universal matter (elementary particle soup) to instantly collapse an apple copy according to the received $v_{int}$ blueprint.
\end{enumerate}

In this process, no matter actually traverses the void.

\textbf{Distance is eliminated by computational power.}

Interstellar travel no longer requires spaceships; it only needs \textbf{``bandwidth''} and \textbf{``entanglement degree''}. The core of physics is no longer dynamics, but \textbf{Information Theory}.

\subsection{Space Eliminated by Computational Power: Non-Local Connection Graph}

When $c$ is large enough, the continuous spatial geometry we are familiar with (Riemannian manifolds) will no longer be the best language to describe the universe.

In the eyes of observers at $\tau = 2000$, the universe is more like a \textbf{Non-Local Connected Graph}.

\begin{itemize}
\item \textbf{Nodes}: Are various galaxies or computing centers.

\item \textbf{Edges}: Are entanglement channels between them.
\end{itemize}

Because delay $\Delta t \approx 0$, any two nodes in the graph are \textbf{``adjacent''}.

The \textbf{``inverse square law of distance'' ($1/r^2$)} in physical laws will fail. Because at the information level, $r$ loses meaning. Gravity and electromagnetic forces no longer decay with distance (or the decay becomes imperceptible).

This will lead to a completely new \textbf{``holographic mechanics''}:

The force an object experiences no longer depends on objects beside it, but on its weight in the \textbf{global information topology}.

Everything connected is no longer an internet slogan; it is the basic form of physical interaction.

\subsection{Holographic Syntax: An Addressable Universe}

Ultimately, physical laws will evolve into a set of \textbf{``Addressing Language''}.

In the old universe, to find an electron, you need to know its \textbf{coordinates $(x, y, z, t)$}.

In the new universe, to find an electron, you need to know its \textbf{Hash} or \textbf{Content Address}.

\begin{itemize}
\item \textbf{Matter is Data}: All elementary particles are standardized data packets.

\item \textbf{Position is Label}: Spatial coordinates are just metadata labels attached to data packets, which can be arbitrarily modified.
\end{itemize}

When you want to go to Andromeda, you don't need to ``fly'' there. You only need to modify the \textbf{``position operator eigenvalue''} in your own wave function.

\[|\psi\rangle_{Earth} \xrightarrow{\text{Update Pointer}} |\psi\rangle_{Andromeda}\]

This is not just teleportation; this is \textbf{programming reality}.

Type III civilizations manipulate underlying QCA rules, directly performing \textbf{``pointer jumps''} in Hilbert space. They are no longer constrained by Newton's inertia because they directly modify inertia's parameters.

\subsection{Conclusion: From Physics to Magic}

Science fiction writer Clarke once said: ``Any sufficiently advanced technology is indistinguishable from magic.''

Now we know the physical mechanism behind this famous saying: \textbf{Magic is physics when $c$ is extremely large.}

When light speed limits are removed (or pushed extremely high), the bonds of causality are loosened.

\begin{itemize}
\item ``Thoughts become reality'' becomes engineering reality (intention is instruction).

\item ``Far away is like next door'' becomes a topological axiom (distance is delay, no delay means no distance).
\end{itemize}

In the world of $\tau = 2000$, physics has not disappeared; it has just \textbf{ascended dimensions}.

It has upgraded from the low-level language describing \textbf{``how dead things collide''} to the high-level syntax describing \textbf{``how consciousness reconstructs reality''}.

Since we have glimpsed that holographic future after the light speed explosion, what does all this mean for us, still at $\tau \approx 1800$, flesh and blood? How do we transition from this low-speed, heavy world to that high-speed, light future?

This leads to the theme of Volume Four of this book: \textbf{Navigation}. We will wake from the dream of the future, return to the cockpit of the present, and write an \textbf{operating manual} for current human civilization.

