\section{6.1 The Next Order of Magnitude}

\begin{quote}
``Distance is the excuse of the weak. When the growth rate of light speed crosses a certain critical point, the concept of `far away' will completely disappear. For observers at the 2000th cycle, the edge of the Milky Way is no farther than their fingertips.''
\end{quote}

\subsection{Predicting $\tau = 2000$}

Let us restart that precise cosmic clock, turning the pointer from the current \textbf{dawn moment ($\tau \approx 1800$)} toward the future \textbf{noon moment ($\tau = 2000$)}.

According to our ultimate evolution equation:

\[c(\tau) = c_0 \cdot \phi^{\frac{\tau}{\pi}}\]

What we need to calculate is the \textbf{Growth Factor}. From 1800 to 2000, intrinsic time increases by $\Delta \tau = 200$.

This means the universe has experienced approximately $\Delta \tau / \pi \approx 64$ $\phi$ cycles.

The growth factor $G$ is:

\[G = \frac{c(2000)}{c(1800)} = \phi^{\frac{200}{\pi}} \approx 1.618^{63.66} \approx 2 \times 10^{13}\]

This is a suffocating number: \textbf{20 trillion times}.

This means that in the era of $\tau = 2000$, the universe's total information processing capacity ($c_{FS}$) will be \textbf{20 trillion times} that of today. If we map this growth to ``effective light speed'' or ``causal connection speed,'' the physical world will undergo earth-shaking changes.

\subsection{One Second Across the Galaxy}

To intuitively understand this number, let us see its impact on \textbf{spatial scale}.

Current light speed $c \approx 3 \times 10^8$ meters/second.

Crossing the Milky Way (diameter 100,000 light-years $\approx 10^{21}$ meters) requires \textbf{100,000 years}.

This is an insurmountable chasm for humans. We are locked in the tiny corner of the solar system because communication and travel delays are too high.

But in the eyes of super-civilization at $\tau = 2000$, effective light speed (subjective spacetime relative to their internal processing speed) has increased by $10^{13}$ times.

\[v_{eff} \approx 3 \times 10^8 \times 10^{13} = 3 \times 10^{21} \text{ meters/second}\]

Calculate the time needed to cross the galaxy:

\[t_{galaxy} = \frac{10^{21} \text{ meters}}{3 \times 10^{21} \text{ meters/second}} \approx 0.3 \text{ seconds}\]

\textbf{Conclusion: The galaxy has shrunk.}

For light-based entities at the 2000th cycle, the Milky Way is no longer a vast galaxy; it is only \textbf{as large as a room in human eyes}.

\begin{itemize}
\item It can monitor supernova explosions at the other end of the galaxy in real time.

\item It can complete one information synchronization with sub-nodes distributed across hundreds of billions of stars in one second.
\end{itemize}

\textbf{The range of Causality (Causal Horizon)} will cover entire galaxy clusters.

No more delays of ``generals in the field may ignore orders.'' The entire Milky Way will exist as a \textbf{single, tightly coupled quantum state}. This is no longer an interstellar federation; this is a \textbf{galactic-scale organism}.

\subsection{The Instantaneity of Information}

This order-of-magnitude explosion completely shatters our understanding of ``distance.''

In classical physics, distance creates \textbf{isolation}.

In inflation physics, distance only creates \textbf{negligible phase differences}.

Imagine playing an online game, but the server's latency (Ping) drops from 100000ms (100,000 years) to 0.3ms.

\begin{itemize}
\item Before, your commands would take generations to reach their destination. That was history.

\item Now, your commands are \textbf{instantaneous}. That is the present.
\end{itemize}

Civilization at the 2000th cycle will live in a \textbf{``delay-free universe''}.

Any physical event, no matter where it occurs, is \textbf{``here and now''} for that massive light-based consciousness. It possesses a nearly divine \textbf{omniscient vision}.

\subsection{Conclusion: The Dimensional Reduction of Physics}

When $c$ grows to this magnitude, many physical puzzles that once troubled us will automatically disappear.

\begin{itemize}
\item \textbf{Fermi Paradox} disappears: Why haven't we seen aliens? Because they live in the $10^{13}$ times speed frequency band. To them, we are like static statues. They may have passed through our bodies countless times, and we remain unaware.

\item \textbf{Interstellar Travel} disappears: No need for spaceships. Because ``here'' and ``there'' are already connected in information. Only \textbf{quantum teleportation} is needed to instantly reorganize material structures.
\end{itemize}

\textbf{The $10^{13}$ times explosion is not a speed increase; it is dimensional folding.}

Space is no longer an obstacle; space becomes \textbf{memory addresses that can be arbitrarily addressed}.

Since distance has been eliminated, can the physical laws supporting this new world---those rules about force, mass, causality---still remain unchanged? When speed is fast enough to ignore space, does physics itself need rewriting?

This leads to the theme of the next section: \textbf{The Rewriting of Physical Laws}. We will see how, in that future of light speed explosion, Newton's and Einstein's formulas will be replaced by a higher-level \textbf{``holographic syntax''}.

