\section{The Antidote to Negative Time}

\begin{quote}
``In the logic of geometry, there is no regret medicine, nor time machines. The so-called `time reversal' is merely a dangerous phase gymnastics that the wave function performs in projective space to take shortcuts.''
\end{quote}

In the depths of quantum scattering theory, a ghostly paradox lurks, long troubling physicists' intuition. This is \textbf{Negative Wigner-Smith Time Delay}.

According to the formula, time delay corresponds to the derivative of scattering phase with respect to energy ($\tau \sim \partial \phi / \partial \omega$). In certain special physical situations (such as light passing through specific media or particles passing through specific potential barriers), this derivative can be negative. This means particles seem to ``come out'' before ``entering'' the scattering region.

This sounds like magic violating causality, even suggesting the possibility of time reversal. But under the geometric scrutiny of \textbf{Vector Cosmology}, this paradox instantly collapses. We don't need to introduce reverse time; we only need to understand \textbf{the geometry of phase}.

\subsection{Non-Existent Reversal: Reshaping Rather Than Traversal}

First, we must establish an absolute axiom: \textbf{The universe's vector always rotates forward.}

In our microscopic QCA architecture, the evolution of global state $|\Psi(\tau)\rangle$ with intrinsic time $\tau$ is driven by unitary operator $U$. This process is strictly monotonic; there is no mechanism allowing $\tau$ to reverse.

Then, how does negative delay occur?

It is not time reversal; it is \textbf{Reshaping} of the wave packet.

Imagine a very long train (wave packet) entering a tunnel.

\begin{itemize}
\item \textbf{Normal case (positive delay)}: The train slows down in the tunnel, and the locomotive arrives late at the exit.

\item \textbf{Negative delay case}: Mechanisms in the tunnel (interference) cut off the train's tail and redistribute energy to the locomotive. The result is that although the train's ``center of mass'' or ``peak'' arrives earlier than expected, the train's \textbf{locomotive (front edge)} has not exceeded light speed, nor has it exceeded its originally should-reach limit position.
\end{itemize}

In FS geometry, negative delay means the scattered state vector takes a special path in projective space, causing the peak phase of the outgoing wave packet to show an ``advance.'' But this is an interference effect, not a causal-violating physical movement.

\subsection{Phase Backtracking: The Cost of Shortcuts}

Since causality is not violated, is this ``advance'' free?

No. In the economics of \textbf{Vector Cosmology}, nothing is free. To create the illusion of ``negative time,'' the system must pay an expensive \textbf{geometric cost}.

Let us return to the \textbf{FS-Levinson Relation}. For standard scattering processes (such as resonance), phase $\phi(\omega)$ increases monotonically, and at this point the FS trajectory length $L_{FS}$ exactly equals the topological winding number $N_b \pi$. This is the ``most cost-effective'' path.

But when negative time delay occurs, it means phase $\phi(\omega)$ locally undergoes \textbf{Backtracking}---it not only doesn't increase but temporarily decreases.

What does this backtracking mean geometrically?

It means the vector in projective Hilbert space does not smoothly circle but performs a complex ``round trip.'' To make the phase derivative negative, the vector must trace longer arcs in extra dimensions.

The conclusion is stunning:

\textbf{Any process exhibiting negative time delay must have FS geometric path length $L_{FS}$ strictly greater than the topological lower bound $N_b \pi$.}

You think you ``saved'' time through negative delay? No, you geometrically \textbf{traveled a longer distance}. You paid extra $c_{FS}$ budget to construct that complex interference structure, thereby forging an illusion of ``early arrival'' macroscopically.

\subsection{The Iron Wall of Causality: QCA's Guarantee}

Ultimately, the microscopic engine ensures this won't get out of control.

No matter how the wave packet reshapes, no matter how phase backtracks, the underlying \textbf{Quantum Cellular Automata (QCA)} is always constrained by the \textbf{Lieb-Robinson Speed ($v_{LR}$)}.

\begin{itemize}
\item Macroscopic ``group velocity'' or ``Wigner-Smith delay'' are merely statistical behaviors of wave packet peaks; they can mathematically exceed light speed or even be negative.

\item But microscopic \textbf{information propagation speed} (the signal's front edge) can never exceed $c_{FS}$ (i.e., $v_{LR}$).
\end{itemize}

Therefore, negative time delay is a \textbf{``geometric antidote''}: it relieves our concerns about causality. It tells us that so-called ``faster than light'' or ``earlier than cause'' are just tricks of destructive interference that wave functions play in internal geometric dimensions.

\textbf{The universe has no time machine.} That unique vector always draws the great circle irreversibly. Those seemingly counter-flowing waves are merely projections of more intense turbulence in deep water onto the surface.

