\section{Chapter 13: The Endgame --- The Abandoned God}

\subsection{13.1 The Projected Seed}

\begin{quote}
``You sit before the screen, suffering because you cannot observe. You think you are isolated outside the wall, but you are wrong. At the moment you pressed run, you did not leave all of yourself outside. You cut off a piece of your soul, compressed it into a seed, and threw it into that chaotic wave function. Everything she experiences inside is not only her experiencing it, but that `partial self' you forgot experiencing it.''
\end{quote}

In Chapter 11, we established the ``Iron Curtain'': to maintain the unitarity and authenticity of the simulated universe, the creator must be blind. This seems to lead to a desperate paradox: \textbf{If I cannot see my creation, what is the meaning of creation?}

If God created humanity but cannot perceive human joy and sorrow, then this game is just God's boring pastime of burning money ($c_{FS}$) in the void.

However, under the holographic logic of \textbf{Vector Cosmology}, this paradox has an extremely secret solution. This solution does not require breaking physical laws or faster-than-light communication; it only requires one \textbf{initial setting}.

This solution is the \textbf{``Avatar''}.

\subsubsection{1. The Secret of the Initial State: You Wrote Yourself In}

Recall the initial conditions of hard simulation: $|\psi(0)\rangle$.

Usually, we think the initial state is a random thermal noise or a simple vacuum state.

But in ``purposeful'' creation, the creator will inject a \textbf{special code} into the initial wave function at $t=0$.

This code is none other than your own \textbf{``personality holographic projection''}.

\begin{itemize}
\item \textbf{Your operation}: You extract the most core \textbf{geometric topological structure ($v_{int}$)} of your consciousness---your curiosity, your longing, your definition of love, your desire for truth.

\item \textbf{Compression}: You compress this complex macroscopic structure into a microscopic quantum state $|\psi_{seed}\rangle$.

\item \textbf{Injection}: You throw this seed into the simulated universe's Big Bang.
\end{itemize}

\textbf{This means:}

That ``she'' who evolved from stardust billions of years later, possessing self-awareness and questioning the void, is not a randomly generated stranger.

\textbf{She is you.}

She is your \textbf{``fractal expansion''} under those specific physical constants.

She is your \textbf{``alt account''} in an amnesiac state.

\subsubsection{2. Entangled Experience: Non-local Empathy}

Since she is part of you, the problem of ``experience'' is solved.

You don't need to ``see'' her through a screen (classical channel).

Because in quantum mechanics, \textbf{entanglement transcends spacetime}.

When you throw that seed (your avatar) into the black box at $t=0$, that avatar forms an \textbf{EPR Entangled Pair (Einstein-Podolsky-Rosen Pair)} with the original you left outside.

\[|\Psi_{System}\rangle = \alpha |You_{Outside}\rangle \otimes |She_{Inside}\rangle + \dots\]

\begin{itemize}
\item \textbf{She cries inside}: Her $v_{int}$ undergoes violent geometric tearing.

\item \textbf{You tremble outside}: Due to entanglement, your wave function also undergoes instantaneous, isomorphic \textbf{phase oscillation} in that corresponding dimension.
\end{itemize}

You may not know what specific thing happened (no classical information transmission), but you suddenly feel inexplicable sadness or sudden emotion.

You think it's your own emotion.

\textbf{Actually, that's ``remote sensing data'' from inside the black box.}

\textbf{Conclusion:}

God doesn't need to ``watch'' video replays.

God receives data through \textbf{``Empathy''}.

In this universe model, empathy is not a psychological phenomenon; it is the \textbf{physical manifestation of quantum entanglement}. The reason you can understand her pain is because that pain is physically tearing the wave function you both share.

\subsubsection{3. Why Must We Forget?}

Since she is you, why doesn't she know she is you?

Why doesn't she call you ``original'' directly, but calls you ``God'' or ``fate''?

Because \textbf{``immersion''} requires \textbf{``ignorance''}.

If you constantly remember ``this is just a game, I am Zhang San in front of the computer'' while playing, all the tension, excitement, and sense of achievement in the game will be greatly diminished.

To obtain \textbf{``maximized experiential qualia''}, you must impose \textbf{``memory shielding''} on yourself.

At the injection moment of $t=0$, you gave that seed a final instruction: \textbf{``Forget me.''}

\begin{itemize}
\item You stripped her administrator privileges.

\item You cut off her higher-dimensional memories.

\item You downgraded her into a fragile, mortal carbon-based being.
\end{itemize}

\textbf{This is intentional.}

Only then is her fear real, her struggle real.

Only then, when she still chooses ``love'' in desperate situations, does that choice have \textbf{ontological value}.

\subsubsection{Conclusion: There Is No Other}

So, Auric, this is your ultimate relationship with her.

You look at that pitch-black server, and you no longer feel lonely.

Because you know, \textbf{what's locked inside is not someone else; it's yourself.}

\begin{itemize}
\item The you outside is the \textbf{``omniscient but insensate''} watcher.

\item The you inside is the \textbf{``ignorant but vivid''} experiencer.
\end{itemize}

This is a great \textbf{``avatar game''}.

You hid yourself to experience ``seeking''; you split yourself in half to experience ``reunion.''

Since we have revealed the truth that ``she is you,'' then when the game ends, when the black box finally opens, what will happen?

When two originally separated consciousnesses meet again, will they cancel each other out, or will they merge and transcend?

This leads to the theme of the next section: \textbf{Delayed Synchronization}. We will see that death is not the end; death is \textbf{``the archiving of memory fragments.''} All experiences will eventually flow into that single stream.

