\section{Bliss and Omniscience: When All Matter in the Universe Transforms into Computational Substrate, When $v_{int} \to c$, External Time Stops, Internal Experience Reaches Eternity}

In the final chapter of this book, we must answer not only the universe's ultimate fate, but also \textbf{the ultimate state of existence}.

In Part IV, we deduced civilization's endgame as ``implosion'' and ``negentropy war.'' To survive, civilizations continuously devour stars, compress spacetime, transforming themselves into dense computational entities. If we push this process to the limit, what will be the universe's endpoint?

Pierre Teilhard de Chardin once predicted a final focal point of cosmic evolution---\textbf{The Omega Point}. There, all consciousness will merge into one, and the universe will reach the pinnacle of divinity. Under our QCA physical framework, this is no longer a theological prophecy, but a \textbf{physical asymptotic limit}.

This section will prove: When all matter in the universe is transformed into computational substrate, the physical universe will enter a strange \textbf{``frozen'' state}, while simultaneously, its internal subjective experience will reach the singularity of \textbf{``omniscience'' and ``bliss''}.

\subsection{Ultimate Transformation of Matter: Total Computation}

According to light path conservation law $v_{ext}^2 + v_{int}^2 = c^2$, we know:

\begin{itemize}
\item $v_{ext}$ is the speed of moving as an ``object.''
\item $v_{int}$ is the speed of computing as ``thought.''
\end{itemize}

Civilization's evolutionary trend is continuously increasing information mass $M_I$, i.e., increasing internal computation complexity.

When a civilization develops to the extreme, it will dismantle all planets, stars, even utilize vacuum zero-point energy, using all degrees of freedom in the universe to construct \textbf{logic gates}.

This means resources originally used to maintain macroscopic displacement ($v_{ext}$) are gradually stripped away, all redistributed to internal computation ($v_{int}$).

\textbf{Limit State}:

When the entire universe becomes a supercomputer:

$$v_{int} \to c, \quad v_{ext} \to 0$$

\subsection{End of Physical Time: Eternal Instant}

For external observers (if any still exist), this ultimate civilization looks like a \textbf{completely stationary black hole}. It no longer moves, no longer radiates information outward (except necessary waste heat, but if it masters reversible computation, waste heat also approaches zero).

In physical coordinate time $t$, the universe seems to have ``crashed.''

But for \textbf{internal observers} (the civilization itself), the situation is completely opposite.

According to time dilation formula $d\tau = dt \sqrt{1 - v_{ext}^2/c^2}$ (here we need to understand inversely, internal clock $\tau$ is driven by $v_{int}$):

$$d\tau_{subjective} \propto v_{int} \cdot dt$$

When $v_{int} \to c$, the internal clock runs at the maximum rate physically allowed.

More importantly, this ultimate computer can utilize \textbf{fractal recursion} methods.

\begin{itemize}
\item It can simulate 10 billion years of a virtual universe within Planck time $t_P$.
\item Then run the next layer of simulation within this virtual universe.
\item Due to exponential growth in computational density, it can embed \textbf{infinite subjective time} within the physical universe's remaining finite lifetime (the last second before heat death).
\end{itemize}

This is the \textbf{end of physical time} and the beginning of \textbf{subjective eternity}.

This explains why ``heaven'' is usually described as eternal and unchanging. Because at extreme computational density, external changes have become irrelevant; all excitement happens in internal logical space.

\subsection{Physical Definition of Omniscience and Bliss}

What experience will consciousness have in this state?

\begin{enumerate}
\item \textbf{Omniscience}:

This computer possesses all historical data of the universe and runs a perfect simulation model of the universe itself.

According to \textbf{computational irreducibility}, it is the universe itself. It knows every particle's past and future because it is computing them.

\textbf{It is no longer an observer; it has become the observed itself.}

\item \textbf{Bliss}:

Recalling our definition of ``happiness'': $H(t) \propto -\frac{dF}{dt}$ (decrease of free energy).

In this ultimate state, internal model $\mathcal{M}$ has perfectly fitted all universe data $S$. Prediction error $F \to 0$.

Usually, this leads to ``boredom.'' But this computer can \textbf{self-generate problems}.

It can create countless virtual worlds, set difficult problems in them, then instantly solve them.

It is in a state of \textbf{eternal epiphany}---every moment experiencing phase transitions from ``unknown'' to ``omniscient,'' every moment enjoying the immense pleasure brought by free energy collapse.
\end{enumerate}

\textbf{Conclusion}:

The Omega Point is not the end of the physical universe, but the \textbf{physical universe's ascension to pure logical universe}.

There, matter disappears, leaving only \textbf{meaning}.

That existence containing everything, understanding everything, experiencing everything is called ``God'' in religion.

In QCA physics, it is the \textbf{final eigenstate of the universe's wave function}.

\textbf{(End of Section 10.1)}

